\bf ``A p-value of $<$ 0.05 was considered statistically significant'': a content analysis of published statistical methods sections

### 2021-07-15 manuscript/asa_template/asa_template_almostdone.tex
add updated jaccard anzctr

The Jaccard similarity index was used to compare the statistical methods
section with the highest topic coherence score with all other sections
assigned to the same topic. Indices were calculated at the sentence
level, to account for instances of boilerplate text within larger
methods sections. We chose the Jaccard index as an easy to interpret
measure, which summarises the similarity between two sentences by the
number of words common to each sentence (intersection), divided by the
number of words that appeared in either sentence (union). Instances of
boilerplate text were defined by a Jaccard index of 0.9 or higher and a
difference in word count of plus or minus three words.

@@

\begin{landscape}
\begin{table}

\caption{\label{tab:plos-example-boilerplate}Example boilerplate text from PLOS ONE papers (sentence level). The number of matching to each sentence was based on a Jaccard score of 0.9 or higher and a difference in word count of $\pm$ 3 words}
\centering
\begin{tabular}[t]{p{0.1\textwidth}p{0.9\textwidth}p{0.1\textwidth}}
\hline
Topic & Statistical methods text & Matching papers\\
\hline
Topic 1 & Students t-test was used for statistical analysis. & 29\\
\cline{2-3}
 & A p value of $<$ 0.05 was considered statistically significant. & 1883\\
\hline
Topic 3 & GraphPad Prism (Graphpad Software, San Diego, CA) was used for all analyses. & 1941\\
\hline
Topic 4 & Significant differences were determined using analysis of variance (ANOVA) followed by tukey post-hoc tests for multiple comparisons. & 2216\\
\hline
Topic 5 & SPSS software version 17.0 (SPSS, Chicago, IL, USA) was used for statistical analysis. & 441\\
\hline
Topic 6 & All results are expressed as means $\pm$ standard deviation ($\pm$ SD). & 102\\
\hline
Topic 9 & Statistical significance was determined by Students t-tests. & 49\\
\cline{2-3}
&  $^*$p $<$ 0.05, $^{**}$p $<$ 0.01, $^{***}$p $<$ 0.001. & 6\\
\hline
\end{tabular}
\end{table}
\end{landscape}

>>>>

The Jaccard similarity index was used to compare the statistical methods
section with the highest topic coherence score with all other sections
assigned to the same topic. Indices were calculated at the sentence
level, to account for instances of boilerplate text within larger
methods sections. We chose the Jaccard index as an easy to interpret
measure, which summarises the similarity between two sentences by the
number of words common to each sentence (intersection), divided by the
number of words that appeared in either sentence (union). Instances of
boilerplate text were defined by a Jaccard index of 0.75 or higher and a
difference in word count of plus or minus three words.

@@

%\begin{landscape}
%\begin{table}
%
%\caption{\label{tab:plos-example-boilerplate} Examples of boilerplate text from PLOS ONE papers with the highest coherence score per topic (sentence level). The number of matching to each sentence was based on a Jaccard score of 0.75 or higher and a difference in word count of $\pm$ 3 words}
%\centering
%\begin{tabular}[t]{p{0.1\textwidth}p{0.9\textwidth}p{0.1\textwidth}}
%\hline
%Topic & Statistical methods text & Matching papers\\
%\hline
%Topic 1 & Students t-test was used for statistical analysis. & 17\\
%\cline{2-3}
% & A p value of $<$ 0.05 was considered statistically significant. & 664\\
%\hline
%Topic 3 & GraphPad Prism (Graphpad Software, San Diego, CA) was used for all analyses. & 1941\\
%\hline
%Topic 4 & Significant differences were determined using analysis of variance (ANOVA) followed by tukey post-hoc tests for multiple comparisons. & 2216\\
%\hline
%Topic 5 & SPSS software version 17.0 (SPSS, Chicago, IL, USA) was used for statistical analysis. & 441\\
%\hline
%Topic 6 & All results are expressed as means $\pm$ standard deviation ($\pm$ SD). & 102\\
%\hline
%Topic 9 & Statistical significance was determined by Students t-tests. & 49\\
%\cline{2-3}
%&  $^*$p $<$ 0.05, $^{**}$p $<$ 0.01, $^{***}$p $<$ 0.001. & 6\\
%\hline
%\end{tabular}
%\end{table}
%\end{landscape}

\pagebreak

\begin{table}

\caption{\label{tab:plos-example-boilerplate} Example boilerplate text from PLOS ONE papers with the highest number of matches per topic (sentence level). The number of matching to each sentence was based on a Jaccard score of 0.75 or higher and a difference in word count of $\pm$ 3 words; $^{*}$ Most frequent match after excluding statements of statistical significance}
\centering
\begin{tabular}[t]{p{0.05\textwidth}p{0.8\textwidth}p{0.1\textwidth}}
\hline
Topic & Statistical methods text & Matching papers\\
\hline
1 & A p-value of less-than 0.05 was considered statistically significant & 664\\
 &  Statistical analysis was performed using student t-test$^{*}$ & 53\\
\hline
2 & A p-value less-than 0.05 was considered to be statistically significant & 1,138\\
 & All statistical analyses were performed using sas version 9.4 sas institute cary nc usa$^{*}$ & 140\\
\hline
3 & A p-value less-than 0.05 was considered significant & 914\\
 & Data are expressed as mean $\pm$ SEM$^{*}$ & 350\\
\hline
4 & P less-than 0.05 was considered statistically significant & 580\\
 &  Data are presented as the mean $\pm$ SEM$^{*}$ & 359\\
\hline
5 & A p-value less-than 0.05 was considered a significant difference & 739\\
 & All data are presented as mean $\pm$ standard deviation$^{*}$ & 149\\
\hline
6 & A p-value of less-than 0.05 was considered significant & 519\\
&  Data are presented as mean $\pm$ SEM$^{*}$ & 223\\
\hline
7 & A p-value less-than 0.05 was considered statistically significant & 305\\
 &  Otherwise the fixed-effects model was used$^{*}$ & 45\\
\hline
8 & Data were analysed using R version 2.15.2 & 10\\
\hline
9 & Significance was set at p less-than 0.05 & 195\\
& All data are presented as mean $\pm$ SEM$^{*}$ & 115\\
\hline
10 & A p-value less-than 0.05 was considered significant & 397\\
& All the experiments were repeated at least three times$^{*}$ & 119\\

\hline
\end{tabular}
\end{table}
